---
title: "MAPS"
author: "Kenneth Kin Pomeyie"
date: "8/17/2021"
output: pdf_document
---


#Load packages and functions
```{r}
library(rnaturalearth) #returns world coastline at specified scale
library(albersusa)  # returns U.S. state composite map  #devtools::install_github("hrbrmstr/albersusa")
library(sf)


Remove_na_cols <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```


#Load data
```{r}
#load rtl data of respective stations
RTL = combined_duration2345
#stations = read.csv("../data/stations.csv")
combined_geo <- left_join(x = RTL, y = stations, by = "ID") %>%
    dplyr::select(ID, Station, State, LONGITUDE, LATITUDE, duration, RTL_2.5, RTL_3.0,  RTL_3_RATIO, RTL_3.25, RTL_3.5)
combined_geo
```

#get coastal and world map as spatial objects
```{r}
coast_sf = ne_coastline(scale = "medium", returnclass = "sf")
countries_sf = ne_countries(scale = "medium", returnclass = "sf")
```








#######################################################################################################################################
########################################DURATION 2###################################################################################
#######################################################################################################################################


#Subset duration of 2 days
```{r}
combined_geo2 = combined_geo %>% 
  filter(duration == 2)

combined_geo2 = Remove_na_cols(combined_geo2, "RTL_3_RATIO")
```

#create sf object with geodata
```{r}
points_sf2 = st_as_sf(combined_geo2, coords = c("LONGITUDE", "LATITUDE" ), crs = 4326)
```


#map of RTL3 RATIO
```{r}
ggplot() +
  geom_sf(data = usa_sf()) +
  geom_sf(data = points_sf2, aes(RTL_3_RATIO, colour = cut(RTL_3_RATIO, c(0.4, 0.9999, 1.5, 2, 10))), alpha = 1, size = 2) +
  coord_sf(xlim=c(-125, -67), ylim=c(20,50))+
  scale_color_manual(name = "RATIO",
                     values = c( "#440154FF",
                                   "#31688EFF",
                                 "#35B779FF",
                                "#FDE725FF"),
                     labels = c( "(0.5, 1)", "[1, 1.5]", "(1.5, 2]", "(2, 5.5)"  )) +
  ggtitle("RTLs for Duration of 2 days")
```




#######################################################################################################################################
########################################DURATION 3###################################################################################
#######################################################################################################################################


#Subset duration of 2 days
```{r}
combined_geo3 = combined_geo %>% 
  filter(duration == 3)

combined_geo3 = Remove_na_cols(combined_geo3, "RTL_3_RATIO")
```

#create sf object with geodata
```{r}
points_sf3 = st_as_sf(combined_geo3, coords = c("LONGITUDE", "LATITUDE" ), crs = 4326)
```


#map of RTL3 RATIO
```{r}
ggplot() +
  geom_sf(data = usa_sf()) +
  geom_sf(data = points_sf3, aes(RTL_3_RATIO, colour = cut(RTL_3_RATIO, c(0.4, 0.9999, 1.5, 2, 10))), alpha = 1, size = 2) +
  coord_sf(xlim=c(-125, -67), ylim=c(20,50))+
  scale_color_manual(name = "RATIO",
                     values = c( "#440154FF",
                                   "#31688EFF",
                                 "#35B779FF",
                                "#FDE725FF"),
                     labels = c( "(0.5, 1)", "[1, 1.5]", "(1.5, 2]", "(2, 7)")) +
  ggtitle("RTLs for Duration of 3 days")
```




#######################################################################################################################################
########################################DURATION 4###################################################################################
#######################################################################################################################################


#Subset duration of 4 days
```{r}
combined_geo4 = combined_geo %>% 
  filter(duration == 4)

combined_geo4 = Remove_na_cols(combined_geo4, "RTL_3_RATIO")
```

#create sf object with geodata
```{r}
points_sf4 = st_as_sf(combined_geo4, coords = c("LONGITUDE", "LATITUDE" ), crs = 4326)
```


#map of RTL3 RATIO
```{r}
ggplot() +
  geom_sf(data = usa_sf()) +
  geom_sf(data = points_sf4, aes(RTL_3_RATIO, colour = cut(RTL_3_RATIO, c(0.4, 0.9999, 1.5, 2, 10))), alpha = 1, size = 2) +
  coord_sf(xlim=c(-125, -67), ylim=c(20,50))+
  scale_color_manual(name = "RATIO",
                     values = c( "#440154FF",
                                   "#31688EFF",
                                 "#35B779FF",
                                "#FDE725FF"),
                    labels = c( "(0.5, 1)", "[1, 1.5]", "(1.5, 2]", "(2, 3.3)")) +
  ggtitle("RTLs for Duration of 4 days")
```





#######################################################################################################################################
########################################DURATION 5###################################################################################
#######################################################################################################################################

#Subset duration of 5 days
```{r}
combined_geo5 = combined_geo %>% 
  filter(duration == 5)

combined_geo5 = Remove_na_cols(combined_geo5, "RTL_3_RATIO")
```

#create sf object with geodata
```{r}
points_sf5 = st_as_sf(combined_geo5, coords = c("LONGITUDE", "LATITUDE" ), crs = 4326)
```


#map of RTL3 RATIO
```{r}
ggplot() +
  geom_sf(data = usa_sf()) +
  geom_sf(data = points_sf5, aes(RTL_3_RATIO, colour = cut(RTL_3_RATIO, c(0.4, 0.9999, 1.5, 2, 10))), alpha = 1, size = 2) +
  coord_sf(xlim=c(-125, -67), ylim=c(20,50))+
  scale_color_manual(name = "RATIO",
                     values = c( "#440154FF",
                                   "#31688EFF",
                                 "#35B779FF",
                                "#FDE725FF"),
                    labels = c( "(0.5, 1)", "[1, 1.5]", "(1.5, 2]", "(2, 6)")) +
  ggtitle("RTLs for Duration of 5 days")
```







